---
title: "Milestone 4"
author: "Katherine Enright"
date: "10/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library("csvy")
library(yaml)
```

```{r read_data}
#I installed the csvy package to read in this file
identity_data <- read_csvy("raw-data/TP190602_EI_final_v1_POP.csvy")

#In the result table, the columnn names are listed as "Q001", "Q002A" etc; I need to figure out which questions in the survey these correspond to.

#The csvy file format is a csv file preceded by a YAML metadata header. The information about the meaning of the question and value codes is contained within this header.

yaml_data <- get_yaml_header("raw-data/TP190602_EI_final_v1_POP.csvy")

#Each column in the csv contains a "name" attribute that is displayed, in addition to "title" (the title of the question), "type" (variable type), and "labels" (possible answers).

#My goal is to link this metadata to the table in identity_data. Is there a way to automatically assign the corresponding question data so that "title" displays instead of "name"?

#I installed the library(yaml) to turn the yaml into R objects. On further exploration, this might not be necessary; I'll keep it around for the time being.

```

```{r initial_plot}
#My goal here is to plot the variable "strength of identity as a Hongkonger" against the age of the participants. One common assumption is that the younger generation in Hong Kong have a stronger unique Hong Kong as opposed to Chinese identity: does the data hold up?

#I chose to use question Q002I as it is an index that combines the values for the two questions on HK identity— "please use a scale of 0-10 to rate your strength of identity as a Hongkonger"(Q002A) and "Please use a scale of 0-10 to rate your importance as a Hongkonger" (Q002B).

#I think a boxplot would be the best way to display this data, as I have discrete x variables (age ranges) and the boxplot will show the distribution of answers by age range.

#Converted the variablefrom a numeric to a factor variable

identity_data$agegp <- as.factor(identity_data$agegp)

plot_data <- identity_data %>%
  select(Q002I, agegp) %>%
  filter(Q002I != "8888", agegp %in% 1:6)

ggplot(plot_data,
  aes(x = agegp, y = Q002I, alpha = 0.3),
  group = agegp
) +
  geom_boxplot(alpha = 0.1, fill = "blue") +
  labs(
    title = "Identity Index of Being a Hong Konger by Age Group",
    x = "Age group",
    y = "Strength of Identity"
  ) +
  geom_jitter(shape = 16, position = position_jitter(0.4), alpha = 0.5, color = "blue") +
  scale_x_discrete(labels = c("18-29", "30-39", "40-49", "50-59", "60-69", "70 or above"))
#Change the X axis labels so they reflect the actual age ranges

#There was an uneven number of responses across the age groups; should I use a weight to account for this?
age_distro <- plot_data %>%
              count(agegp)

#my results didn't match my hypothesis, so I'm going to create a function to compare the average identity score across age groups. On second glance, the data checks out.
avg_by_age <-  function(.x) {
  plot_data %>% 
  filter(agegp == .x) %>%
  summarise(avg=mean(Q002I))
}

#I might also consider comparing the results of this identity index over time.
```

 One common assumption, especially with regards to the current protests, is that the younger generation in Hong Kong have a stronger unique Hong Kong identity as opposed to Chinese identity. The data displayed here in this graph questions that assumption, and shows a fairly consistent high percentage of identification with Hong Kong identity across age groups. The next step of my analysis will be to compare this "Identity Index of Being a Hong Konger" (Q002I) with the "Identity index of being a Chinese citizen" (Q003I).
 
I chose to plot the results of question Q002I in this box plot as it is an index that combines the values for the two questions on HK identity— "please use a scale of 0-10 to rate your strength of identity as a Hongkonger"(Q002A) and "Please use a scale of 0-10 to rate your importance as a Hongkonger" (Q002B).

Source: Survey of Nationality and Identity in Hong Kong, Public Opinion Programme, The University of Hong Kong